\textbf{Computational Fuzzy Extractors}

### 2013-02-26 CompFuzzExt.tex
Added Markov inequality to HILL impossibility

Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a noisy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from noisy computational conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

@@

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.% with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-1,t)$ (information-theoretic) secure sketch with error
$2(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Defining Noisy Computational Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a noisy computational conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a noisy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} if the following properties hold:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

>>>>

Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

@@

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).  Unfortunately, we show that the unpredictability entropy must decrease with the $O(\log B_t(\cdot))$.  
\begin{theorem}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.  Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.  It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.  We begin by showing that $Y$ must correctly recover most of the time.
\begin{claim}
\label{clm:y is recoverable}
\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
\item Input $x\in \zo^b, s\in\zo^*$.
\item Sample $x'\leftarrow B_t(x)$.
\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.  The statement of the claim follows as 
\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.  \clref{clm:y is recoverable} says that 
 \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.  We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
\item Input $s\in\zo^*$.
\item Sample $x'\leftarrow \zo^b$.
\item Output $\rec(x', s)$.
We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
We now show that $\mathcal{I}$ predicts $Y$, defining :
2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The two statements are incomparable.
\subsection{Defining  Computational Fuzzy Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.
